### 2016-09-16 thesis_paper/source.tex
styling
Last known good state

\documentclass[11pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[dvips]{graphicx}
\usepackage{xcolor}
\usepackage{times}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts,amssymb,calc,calrsfs,cleveref}
\usepackage[justification=centering]{caption}
\usepackage{url}
\usepackage{subfigure}
\usepackage{cleveref}

@@

\usepackage{geometry}
% PDF VIEW
\geometry{total={210mm,297mm},
left=25mm,right=25mm,%
bindingoffset=0mm, top=25mm,bottom=25mm}
%PRINT
\geometry{total={210mm,297mm},
left=20mm,right=20mm,
bindingoffset=0mm, top=15mm,bottom=35mm}

@@

\newcommand\frontmatter{%
    \cleardoublepage
  %\@mainmatterfalse
  \pagenumbering{roman}}

\newcommand\mainmatter{%
    \cleardoublepage
 % \@mainmattertrue
  \pagenumbering{arabic}}

\newcommand\backmatter{%
  \if@openright
    \cleardoublepage
  \else
    \clearpage
  \fi
 % \@mainmatterfalse
   }

@@

\renewcommand{\contentsname}{CONTENTS}
\renewcommand{\listfigurename}{LIST OF FIGURES}
\renewcommand{\listtablename}{LIST OF TABLES}
\renewcommand{\abstractname}{ABSTRACT}

\begin{document}
{
\frontmatter

\thispagestyle{empty}

\linespread{1}\selectfont
\centering
\vspace*{5\baselineskip}
Parallelization of Push-based System for

@@

%{ by }
\vspace*{3\baselineskip}

@@

\vspace*{2\baselineskip}
\vspace{.5cm}
Date of Approval:

N/A

@@

\clearpage
\pagestyle{plain}
\centering

\vspace*{5\baselineskip}
\linespread{2}\selectfont
\textbf{DEDICATION}

\begin{flushleft}
\hspace{3em} I dedicate my thesis work to my family who have always been supporting me throughout my life. I also dedicate it to my closest friends who have shared my passion and encouraged me to explore and try my ideas in life.
\end{flushleft}

@@

\pagestyle{plain}
\centering

\textbf{ACKNOWLEDGMENTS}

\begin{flushleft}
\hspace{3em} I would like to thank my major professor throughout my master thesis Dr. Yicheng Tu for his guidance and knowledge that I received through all the time I worked with him. I really appreciate his contribution and very happy that I got a chance to work with him. I as well want to thank the committee members for their support and encouragement.
\end{flushleft}

@@

\linespread{1}\selectfont
\tableofcontents

@@

\mainmatter
\linespread{1}\selectfont

\chapter{Introduction} \linespread{2}\selectfont \justify

>>>>

\documentclass[12pt,letterpaper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[dvips]{graphicx}
\usepackage{xcolor}
\usepackage{times}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts,amssymb,calc,calrsfs,cleveref}
\usepackage[justification=centering]{caption}
\usepackage{url}
\usepackage{subfigure}
\usepackage{cleveref}

@@

\usepackage{geometry}
\geometry{left=1in,right=1in,top=1in,bottom=1in}

@@

\newcommand\frontmatter{%
    \cleardoublepage
  \pagenumbering{roman}}

\newcommand\mainmatter{%
    \cleardoublepage
  \pagenumbering{arabic}}

\newcommand\backmatter{%
  \if@openright
    \cleardoublepage
  \else
    \clearpage
  \fi
   }

@@

\renewcommand{\contentsname}{TABLE OF CONTENTS}
\renewcommand{\listfigurename}{LIST OF FIGURES}
\renewcommand{\listtablename}{LIST OF TABLES}
\renewcommand{\abstractname}{ABSTRACT}

\begin{document}
{
\frontmatter\thispagestyle{empty}\linespread{1}\selectfont\centering\vspace*{4\baselineskip}
Parallelization of Push-based System for

@@

{ by }

\vspace*{3\baselineskip}

@@

\vspace*{2\baselineskip}
Date of Approval:

August 23, 2016

@@

\linespread{1}\selectfont\clearpage
\thispagestyle{empty}
\centering
\linespread{1}\selectfont
\vspace*{3\baselineskip}
\textbf{DEDICATION}
\linespread{2}\selectfont
\begin{flushleft}
\hspace{3em} I dedicate my thesis work to my family who have always been supporting me throughout my life. I also dedicate it to my closest friends who have shared my passion and encouraged me to explore and try my ideas in life.
\end{flushleft}

@@

\linespread{1}\selectfont\clearpage
\thispagestyle{empty}
\centering
\linespread{1}\selectfont
\vspace*{3\baselineskip}
\textbf{ACKNOWLEDGMENTS}
\linespread{2}\selectfont
\begin{flushleft}
\hspace{3em} I would like to thank my major professor throughout my master thesis Dr. Yicheng Tu for his guidance and knowledge that I received through all the time I worked with him. I really appreciate his contribution and very happy that I got a chance to work with him. I as well want to thank the committee members for their support and encouragement.
\end{flushleft}

@@

\linespread{1}\selectfont
\frontmatter
\tableofcontents

@@

\mainmatter
\linespread{1}\selectfont
\chapter{Introduction} \linespread{2}\selectfont \justify
